---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# smovie  

[![Travis-CI Build Status](https://travis-ci.org/paulnorthrop/smovie.svg?branch=master)](https://travis-ci.org/paulnorthrop/smovie) 
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/paulnorthrop/smovie?branch=master&svg=true)](https://ci.appveyor.com/project/paulnorthrop/smovie)

### Some movies to teach statistical concepts

### What does smovie do?

The `smovie` package provides movies to help students to understand statistical 
concepts.  The [`rpanel` package](https://cran.r-project.org/package=rpanel) is 
used to create interactive plots that move to illustrate key statistical ideas 
and methods.  The movies cover the topics of probability distributions; sampling distributions of the mean (central limit theorem), the maximum (extremal types theorem) and the (Fisher transformation of the) correlation coefficient; simple linear regression; hypothesis testing.

### An example

The function `wws` produces a movie to visualise the Wald, Wilks and score likelihood-based test statistics, for a model with a scalar unknown parameter.  The user can change the value of the parameter under a simple null hypothesis and observe the effect on the test statistics.  The following code uses the log-likelihood from a binomial experiment and considers the null hypothesis that the success probability $\theta$ is equal to $\theta_0$.  The user may specify their own log-likelihood.

```{r, eval = FALSE}
wws(theta0 = 0.5)
```

### Installation

To get the current released version from CRAN:

```{r installation, eval = FALSE}
install.packages("smovie")
```

### Vignettes

See `vignette("smovie-vignette", package = "smovie")` for an overview of the 
package. 

